---
title: "Children's social referencing reflects sensitivity to graded uncertainty"
bibliography: library.bib
csl: apa6.csl
document-params: "10pt, letterpaper"

author-information: > 
    \author{{\large \bf Emily  Hembacher} \\ \texttt{ehembach@stanford.edu} \\ Department of Psychology \\ Stanford University
    \And {\large \bf Benjamin deMayo} \\ \texttt{bedemayo@stanford.edu} \\ Department of Psychology \\ Stanford University
    \And {\large \bf Michael C. Frank} \\ \texttt{mcfrank@stanford.edu} \\ Department of Psychology \\ Stanford University} 

abstract: 
    "The ability to monitor epistemic uncertainty is critical for self-directed learning. However, we still know little about young children's ability to detect uncertainty in their mental representations. Here we asked whether a spontaneous information gathering behavior -- social referencing -- is driven by uncertainty during early childhood. Children ages 2-5 completed a word-learning task in which they were presented with one or two objects, heard a label, and were asked to put the labeled object in a bucket. Referential ambiguity was manipulated through the number of objects present and their familiarity. In Experiment 1, when there were two novel objects and a novel label, the referent was ambiguous; when there were two familiar objects, or only one novel or familiar object, the referent was known or could be inferred. In Experiment 2, there were either two novel objects, two familiar objects, or one familiar and one novel object; in the latter case the referent could be inferred by excluding the familiar object. To further manipulate the availability of referential cues, the experimenter gazed at either the target or the center of the table while labeling the object. In both experiments, children looked at the experimenter more often while making their response when the referent was ambiguous. In Experiment 2, children also looked at the experimenter more when there was one familiar and one novel object, but only when the experimenter's gaze during labeling was uninformative. These results suggest that children's social referencing is a sensitive index of graded epistemic uncertainty."
    
keywords:
    "social referencing; help seeking; word learning; uncertainty."
    
output: cogsci2016::cogsci_paper
---

```{r global_options, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(fig.width=3, fig.height=3, fig.crop = F, fig.pos = "tb", fig.path='figs/',
                      echo=F, warning=F, cache=F, message=F, sanitize = T)
```

```{r, libraries}
library(png)
library(grid)
library(ggplot2)
library(xtable)
library(langcog)
library(dplyr)
library(ggplot2)
library(rjson)
library(stringr)
library(tidyr)
library(lme4)
library(knitr)
library(markdown)
library(lmerTest)
library(ggthemes)
```

Preschoolers quickly learn new concepts, rules, and language. They also actively explore and ask questions in ways that seem targeted to maximize learning [@Chouinard2007; @Schulz2007]. However, we still have an incomplete understanding of young children’s ability to monitor their own mental states, in particular, their epistemic uncertainty [@Sodian2012]. Do preschool-aged children monitor uncertainty and actively guide their learning behaviors on the basis of this monitoring, or is early learning better characterized as a process of integrating information that is largely generated externally, for example, by social partners who act as teachers [@Csibra2006]? 

A hallmark of successful uncertainty monitoring is being less confident when the probability of accuracy is lower [@Robinson1997]. This ability includes awareness of complete ignorance, but also of graded evidence in mental representations, which is considered important for predicting outcomes and regulating behavior [@Lyons2011]. During adulthood, accurately representing one's own learning progress allows for efficient self-directed study and predicts learning outcomes [@Dunlosky2012]. There is mixed evidence about whether young children can accomplish this type of self-monitoring. For example, 3-year-olds report being equally confident about correct and incorrect responses in memory tasks [@Hembacher2014]. Preschoolers report being less confident when they are wrong in other tasks, but they are typically overconfident overall [@Coughlin2015; @Lipowski2013]. However, these studies may underestimate young children's uncertainty monitoring, as they typically rely on explicit metacognitive reports. Children may learn to respond appropriately to uncertainty in everyday learning situations before they can bring it fully into consciousness and report on it.

Several studies have provided evidence that children's spontaneous information-seeking behaviors might track uncertainty. Call and Carpenter [-@Call2001] had 2-year-olds choose between several tubes to find a hidden sticker. They found that the toddlers were more likely to peek inside a tube before choosing when they had not seen the baiting of the tubes compared to when they had, suggesting they were aware of their ignorance and managed to delay their response until they were sufficiently confident. In another study, Goupil, Romand-Monnier, and Kouider [-@Goupil2016] found that 20-month-olds were more likely to seek help by looking at their parents when they were unable to respond accurately in a memory task. These spontaneous information-gathering behaviors may provide a window into early uncertainty monitoring, and allow us to ask questions about its development.

Here, we focus on the role of uncertainty in guiding social referencing -- one form of information gathering -- during word learning. Referencing a social partner can provide several types of disambiguating information. For example, children can follow a speaker's gaze direction to infer the referent of a new word, as people tend to look at objects they are referring to. By the second year of life infants follow a speaker’s gaze and map labels to objects on the basis of gaze direction [@Baldwin1991]. There is also evidence that infants' propensity for gaze-following predicts later language development [@Carpenter1998], highlighting the importance of this behavior for learning. In addition to monitoring gaze direction, children may reference a social partner's emotional reaction to a stimulus or event, which can help disambiguate the appropriateness of a response [@Walden1988]. Finally, looking at a social partner can be taken as a bid for help [@Vredenburgh2015], and may result in explicit instruction.

Social referencing can be an efficient source of disambiguating information, but is it driven by uncertainty during early childhood? It could be that social referencing is not costly enough to require selectivity, or that uncertainty signals are too weak to drive this type of information-seeking behavior in young children. Similarly, other learning mechanisms, such as the privileging of social information [@Ho2017] or tracking of regularities in the environment [@Yurovsky2015], may be sufficiently powerful to obviate the need for self-monitoring of uncertainty. 

The present work adapts a paradigm used by Vaish, Demir and Baldwin [-@Vaish2011] to ask whether preschoolers reference a speaker more frequently when the referent of the speech is ambiguous. In Vaish et al.'s study, 13- to 18-month-olds sat across from an experimenter who produced a label (e.g., “a modi!") in the presence of one or two novel objects. Infants looked towards the experimenter more often when there were two objects present, and the referent was thus ambiguous, suggesting that infants' social referencing is driven by referential uncertainty. 

Here we adapt this procedure for use with preschoolers, who have a richer behavioral repertoire compared to infants, and may or may not actively reference social information based on uncertainty for the reasons discussed previously. In addition to manipulating the number of objects present as in Vaish et al., we manipulate the familiarity of the objects to exclude the possibility that social referencing is driven by visual complexity (i.e., the number of objects present) rather than knowledge representations. If young children's social referencing is driven by awareness of epistemic uncertainty and not visual complexity, we would expect them to look more at the speaker when two novel objects are present, but not when two familiar objects are present, as the referent is unambiguous in the latter case. In Experiment 2, we additionally investigate whether children's social referencing it is sensitive to graded uncertainty by manipulating the amount of disambiguating evidence available to children.

```{r design, fig.env = "figure", fig.pos = "h", fig.align='center', fig.width=3, fig.height=3, set.cap.width=T, num.cols.cap=1, fig.cap = "Study design for Experiments 1 and 2."}
img <- png::readPNG("figs/socref_design.png")
grid::grid.raster(img)
```

# Experiment 1

We first asked whether preschool-aged children’s social referencing reflects sensitivity to uncertainty based on referential ambiguity. In Experiment 1, we examined whether children would reference a speaker more often when they produced a referentially ambiguous label compared to an unambiguous label. Children sat across from an experimenter who labeled an object on the table between them (Figure \ref{fig:design}). After labeling an object, the experimenter asked the child to place the named object in a bucket. Across trials, there were either one or two objects on the table, which were either familiar or unfamiliar to the child. This design allowed us to test whether merely having more than one object present is sufficient to increase social referencing (which could not be ruled out by Vaish et al.), or if referential ambiguity (and thus epistemic uncertainty) is the underlying factor. If the latter is true, we expected children to increase their looking to the experimenter only on trials with two unfamiliar objects, when the object-label mapping was not known and could not be inferred.

We were interested in the amount of social referencing children exhibited across the trial. We considered four different phases of each trial based on the notion that children might expect different social information at different stages of the task. Specifically, we predicted that children might expect the speaker's gaze direction to be informative during the labeling itself, as speakers tend to look at objects they refer to. We predicted that later in the trial, as children reached for an object and placed it in the bucket, children might expect confirmation of the accuracy of their choice. We were interested in whether children would reference the speaker to a greater degree across these phases when referential ambiguity was high, which would indicate sensitivity to epistemic uncertainty. On the other hand, if children's looking is driven by external stimuli and not epistemic uncertainty, we might find that they reference the speaker more when there are two objects present, regardless of familiarity, or when novel objects are present, regardless of the number of objects. 

```{r}
load("soc_ref_e1.RData")

age_months <- d %>%
  group_by(age_years) %>%
  multi_boot_standard(col = "age_months")

age_months$age_years <- factor(age_months$age_years,
levels = c(2, 3, 4, 5),
labels = c("two", "three", "four", "five"))
```

## Methods

### Participants
We recruited a planned sample of 80 children ages 2-5 years from the Children’s Discovery Museum in San Jose, California.^[Planned sample size, exclusion criteria, and analysis plan preregistered at https://osf.io/y7mvt] The sample included 20 2-year-olds (mean age `r round(age_months$mean[age_months$age_years=="two"], digits = 2)` months), 20 3-year-olds (mean age `r round(age_months$mean[age_months$age_years=="three"], digits = 2)` months), 20 4-year-olds (mean age `r round(age_months$mean[age_months$age_years=="four"], digits = 2)` months), and 20 5-year-olds (mean age `r round(age_months$mean[age_months$age_years=="five"], digits = 2)` months). An additional 20 children participated but were removed from analyses because they heard English less than 75% of the time at home (*n* = 10), because they were unable to complete at least half of the trials in the task (*n* = 4), because of parental interference (*n* = 1), or due to experimenter or technical errors (*n* = 5). 

### Stimuli and Design
Children were presented with one or two objects, heard a label, and were asked to put the labeled object in a bucket. Half of the objects were selected to be familiar to children (e.g., a cow) and half were selected to be novel (e.g., a nozzle). There were four trial types: one-familiar, one-novel, two-familiar, and two-novel. There were three trials of each type, for a total of twelve trials. Trial types were presented sequentially in an order that was counterbalanced across participants. The assignment of individual objects to trial types was counterbalanced. On familiar trials, the familiar label for the target object was used (e.g., “cow”). On novel trials, a novel label was used (e.g., “dawnoo”). 

The critical manipulation was of referential ambiguity; on one-familiar and two-familiar trials, there was no referential ambiguity, as children were expected to be certain about the objects and their labels. Similarly, on one-novel trials, children were expected to be certain about the label referent as there was only one option. However, on two-novel trials, the referent was ambiguous, as the novel label could apply to either novel object.

Throughout the task, the experimenter never gazed at the object they were labeling, or responded to children's verbal or non-verbal bids for help by indicating the correct object. Thus, children were expected to remain uncertain about the referent throughout the trial when two novel objects were present. 

### Procedure

Throughout the study, the child sat at one end of a large circular table, and the experimenter stood at the opposite end. Each trial of the task proceeded as follows: the experimenter placed one or two objects on the left and/or right sides of the table, out of reach of the child so that the child could not interact with the toys during the labeling event. For one-object trials, the location of the object (left or right) alternated between trials. 

After placing the objects, the experimenter said “Hey look, there’s a (target) here.” The experimenter gazed at the center of the table rather than the object they labeled (see rationale in Stimuli and Design). The experimenter waited approximately two seconds (based on a visual metronome placed within view) before saying, “Can you put the (target) in the bucket?” They then pushed the object(s) forward within reach of the child, and placed a plastic bucket in the center of the table, also within reach of the child. Prior to the twelve experimental trials, there were two training trials: a one-familiar trial and a two-familiar trial, to acquaint the child with the procedure. A camera placed to the side of the experimenter captured the participant’s face, so that looking behavior could be coded from video.

### Coding procedure

Videos were coded using DataVyu software (http://datavyu.org). For each participant, we coded the number of times they referenced the experimenter across the trial. Because we were interested in the precise circumstances in which children feel uncertain enough to reference a speaker, we coded the number of looks that occurred during four phases of the trial: a *label* phase, which began at the utterance of the label and ended when the experimenter began to slide the objects, a *slide* phase, in which the experimenter slid the object(s) into the child’s reach, a *planning phase*, which began at the end of the slide and ended when the child touched an object, and a *response* phase, which began when the child touched an object and ended when the child released the object into the bucket. A second coder independently scored the number of looks for one third of the trials for each participant to establish reliability.

## Results and Discussion

```{r}
#get means for plot
msslooks <- filter(d, exclude == 0) %>%
  group_by(SID, phase_name, num_objs, familiarity, age_years) %>%
  summarise(num_looks = mean(num_looks))

mslooks <- filter(d, exclude == 0) %>%
  group_by(phase_name, familiarity, num_objs, age_years) %>%
  multi_boot_standard(col = "num_looks") 

msslooks$phase_name <- factor(msslooks$phase_name, levels = c("label","slide", "planning", "response"))
mslooks$phase_name <- factor(mslooks$phase_name, levels = c("label","slide", "planning", "response"))

msslooks$num_objs <- factor(msslooks$num_objs,
levels = c(1,2),
labels = c("One object", "Two objects"))

mslooks$num_objs <- factor(mslooks$num_objs,
levels = c(1,2),
labels = c("One object", "Two objects"))

msslooks$age_years <- factor(msslooks$age_years,
levels = c(2, 3, 4, 5),
labels = c("2 years", "3 years", "4 years", "5 years"))

mslooks$age_years <- factor(mslooks$age_years,
levels = c(2, 3, 4, 5),
labels = c("2 years", "3 years", "4 years", "5 years"))
```


```{r results_e1,fig.width=8, fig.height=6,out.width="5.75in", out.height="4.35in", fig.env='figure*', fig.align='center', fig.pos='h', fig.cap='Results of Experiment 1. Number of looks to the experimenter across phases and conditions. Age in months was entered as a continuous variable in regression models but is presented here as a categorical variable for visual simplicity. Error bars are 95 percent confidence intervals.'}

ggplot(msslooks, aes(x = phase_name, y = num_looks, 
               col = familiarity, group = familiarity)) + 
  geom_line(data = mslooks, aes(y = mean)) + 
  geom_pointrange(data = mslooks, 
                  aes(y = mean, ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width =.1)) + 
  facet_grid(age_years ~ num_objs) +
  scale_y_continuous(limits=c(0,2), breaks=c(0,1,2)) +
  theme(axis.text.x = element_text(angle = 0, hjust = .5, vjust = .5)) + 
  labs(x = "Phase", y = "Number of Looks") +
  ggthemes::theme_few() +
  langcog::scale_colour_solarized() 
  
  
  #+ theme(legend.position = c(0.3, 0.9),legend.background = element_rect(fill = "white", colour = NA))

```

```{r include = FALSE}
lmer_data <- d %>%
  filter(!exclude) %>%
  mutate(num_objs = factor(num_objs), 
         familiarity = factor(familiarity), 
         age_c = as.numeric(langcog::scale(age_months, scale=FALSE)),
         phase_name = factor(phase_name))
```

```{r lmer_e1, results="asis"}
l_lm <- lmer(num_looks ~ num_objs * familiarity * age_c +
             (num_objs * familiarity | SID),
           data = filter(lmer_data, phase_name == "label"))

label_lm <- summary(l_lm)

s_lm <- lmer(num_looks ~ num_objs * familiarity * age_c +
             (num_objs | SID),
           data = filter(lmer_data, phase_name == "slide"))

slide_lm <- summary(s_lm)

p_lm <- lmer(num_looks ~ num_objs * familiarity * age_c +
             (num_objs + familiarity | SID),
           data = filter(lmer_data, phase_name == "planning"))

planning_lm <- summary(p_lm)

r_lm <- lmer(num_looks ~ num_objs * familiarity * age_c +
             (num_objs  | SID),
           data = filter(lmer_data, phase_name == "response"))

response_lm <- summary(r_lm)
```

Results of Experiment 1 are presented in Figure \ref{fig:results_e1}. Inter-rater reliability for the number of looks in each phase was high, intraclass correlation *r* = .97, *p*<.001. To test our prediction that referential ambiguity (i.e., having two novel objects) would produce more social referencing, we fit mixed-effects linear regression models separately for each phase with the following structure: `number of looks ~ number of objects * familiarity * age in months + (number of objects + familiarity | Subject ID)`. A single model with phase as a factor did not converge.

We did not find any main or interaction effects of number of objects, familiarity, or age on number of looks during the label or slide phases. Thus, mere novelty or the presence of multiple objects was not enough to increase social referencing. However, we found an interaction effect of number of objects and familiarity during the planning ($\beta$ = `r round(planning_lm$coefficients[5], digits = 2)`, *p* < .001) and response phases ($\beta$ = `r round(response_lm$coefficients[5], digits = 2)`, *p* < .001), such that 2-novel trials were associated with more looking. There was no interaction with age in either phase.^[https://github.com/emilyfae/socref_uncert] In summary, children looked to the experimenter more often when planning and executing a response under uncertainty. These results suggest that children were aware that they did not have sufficient knowledge to answer independently, and referenced the speaker to resolve this uncertainty.

We did not find the expected effect of referential ambiguity in the label phase. It is possible that children failed to predict that they would need more information until later in the trial, when they were actually faced with making a decision. Another possibility is that children's looking was at ceiling during the labeling phase, perhaps because children look at someone who is speaking regardless of the need for referential disambiguation. A third possibility is that this is an artifact of our design, in which the experimenter gazed at the center of the table rather than the referent of the label. Children may have realized that the experimenter's gaze direction during labeling was not informative. Similarly, children may have found it strange to interact with an experimenter who did not gaze at the object they were labeling, which may have produced unnatural patterns of social referencing. Experiment 2 tests these possibilities and examines whether children's social referencing is sensitive to graded uncertainty.

# Experiment 2

Experiment 2 was designed to replicate Experiment 1 and to investigate whether children's social referencing is sensitive to uncertainty based on graded evidence about a label's referent. Since we did not observe any difference between one-familiar and one-novel trials, we eliminated single-object trials, leaving the 2-familiar and 2-novel trials. In addition, we added 1-novel-1-familiar trials ("mutual exclusivity trials"). For these trials, we expected that children would be able to infer the referent by excluding the familiar object as a possibility. For example, when a toy lion and a novel item were present, they could exclude that the speaker was referring to the lion as a "blicket" [@Markman1988]. We predicted that children might be less certain about their choice on these trials compared to when the label and referent were familiar to them (2-familiar trials), but more confident than when there are no cues to reference (2-novel trials).

In addition, we manipulated between participants whether or not the experimenter's gaze during labeling was informative (they gazed at either the referent of their label or the center of the table), allowing us to determine whether children selectively reference gaze during labeling when gaze is expected to be informative. The manipulation of informativity of gaze during labeling also meant that participants in the referential gaze condition had an additional referential cue, which might decrease uncertainty for the remainder of the trial. In Experiment 1, we did not observe an effect of age on looking. Thus, we restricted the current sample to 3- and 4-year-olds. 

## Methods

```{r}
load("soc_ref_e2.RData")

halfs<- d %>%
  mutate(first_half = between(trial, 1, 4)) 

age_months <- d %>%
  group_by(age_years) %>%
  multi_boot_standard(col = "age_months")

age_months$age_years <- factor(age_months$age_years,
levels = c(3, 4),
labels = c("three", "four"))
```

### Participants

We recruited a planned sample of 80 children ages 3-4 years from the Children’s Discovery Museum in San Jose, California.^[Planned sample size, exclusion criteria, and analysis plan preregistered at https://osf.io/y7mvt/.]. The sample included 40 3-year-olds (mean age `r round(age_months$mean[age_months$age_years=="three"], digits = 2)` months) and 40 4-year-olds (mean age `r round(age_months$mean[age_months$age_years=="four"], digits = 2)` months). An additional 20 children participated but were removed from analyses because they heard English less than 75% of the time at home (*n* = 9), because they were unable to complete at least half of the trials in the task (*n* = 7), or due to experimenter or technical errors (*n* = 4).

### Stimuli and Design

The stimuli and design were similar to Experiment 1, except that we eliminated 1-object trials. Instead, we included three trial types: 2-familiar ("familiar"), 2-novel ("novel"), and 1-novel-1-familiar ("mutual exclusivity"). There were four of each trial type, totaling twelve trials. In addition, we manipulated the experimenter’s gaze behavior between participants. For half of the participants, the experimenter looked at the center of the table while labeling objects; for the remaining half, they looked directly at the objects they labeled.

### Procedure

The procedure was identical to Experiment 1, except that there were three practice trials rather than two, which were comprised of two familiar trials and one novel trial. We included two familiar trials during the practice so that children would experience the satisfaction of picking the correct object and remain motivated to complete the task.

## Results and Discussion

```{r}
#do children look at the speaker more often in the gaze condition as the trials move forward?
msslooks_half <- filter(halfs, exclude == 0) %>%
  group_by(SID, phase_name, trial_type, Gaze, first_half) %>%
  summarise(num_looks = mean(num_looks))

mslooks_half <- filter(halfs, exclude == 0) %>%
  group_by(phase_name, trial_type, Gaze, first_half) %>%
  multi_boot_standard(col = "num_looks") 

msslooks_half$phase_name <- factor(msslooks_half$phase_name, levels = c("label","slide", "planning", "response"))
mslooks_half$phase_name <- factor(mslooks_half$phase_name, levels = c("label","slide", "planning", "response"))

#get means for plot
msslooks <- filter(d, exclude == 0) %>%
  group_by(SID, phase_name, trial_type, Gaze, age_years) %>%
  summarise(num_looks = mean(num_looks))

mslooks <- filter(d, exclude == 0) %>%
  group_by(phase_name, trial_type, Gaze, age_years) %>%
  multi_boot_standard(col = "num_looks") 

msslooks$phase_name <- factor(msslooks$phase_name, levels = c("label","slide", "planning", "response"))
mslooks$phase_name <- factor(mslooks$phase_name, levels = c("label","slide", "planning", "response"))

msslooks$trial_type <- factor(msslooks$trial_type, labels = c("two-familiar","one-novel-one-familiar", "two-novel"))
mslooks$trial_type <- factor(mslooks$trial_type, labels = c("two-familiar","one-novel-one-familiar", "two-novel"))

msslooks$Gaze <- factor(msslooks$Gaze,
levels = c("gaze","no_gaze"),
labels = c("Referential gaze", "No referential gaze"))

mslooks$Gaze <- factor(mslooks$Gaze,
levels = c("gaze","no_gaze"),
labels = c("Referential gaze", "No referential gaze"))

msslooks$age_years <- factor(msslooks$age_years,
levels = c(3, 4),
labels = c("3 years", "4 years"))

mslooks$age_years <- factor(mslooks$age_years,
levels = c(3, 4),
labels = c("3 years", "4 years"))

msslooks <- msslooks %>%
  mutate(familiarity = trial_type)

mslooks <- mslooks %>%
  mutate(familiarity = trial_type)
```


```{r results_e2, fig.width=8, fig.height=5,out.width="5.75in", out.height="3.5in", fig.env='figure*', fig.align='center', fig.pos='h', fig.cap='Results of Experiment 2. Number of looks to the experimenter across phases and trial types. Age in months was entered as a continuous variable in regression models but is presented here as a categorical variable for visual simplicity. Error bars are 95 percent confidence intervals.'}

ggplot(msslooks, aes(x = phase_name, y = num_looks, 
               col = trial_type, group = trial_type)) + 
  geom_line(data = mslooks, aes(y = mean)) + 
  geom_pointrange(data = mslooks, 
                  aes(y = mean, ymin = ci_lower, ymax = ci_upper, shape = trial_type), 
                  position = position_dodge(width =.1)) + 
  facet_grid(age_years ~ Gaze) + 
  scale_y_continuous(limits=c(0,2), breaks=c(0,1,2)) +
  theme(axis.text.x = element_text(angle = 0, hjust = .5, vjust = .5))+ 
  labs(x = "Phase", y = "Number of Looks")  +
  ggthemes::theme_few() +
  langcog::scale_colour_solarized() 


#plot number of looks based on half.
ggplot(msslooks_half, aes(x = phase_name, y = num_looks, 
               col = trial_type, group = trial_type)) + 
  geom_line(data = mslooks_half, aes(y = mean)) + 
  geom_pointrange(data = mslooks_half, 
                  aes(y = mean, ymin = ci_lower, ymax = ci_upper, shape = trial_type), 
                  position = position_dodge(width =.1)) + 
  facet_grid(first_half ~ Gaze) + 
  scale_y_continuous(limits=c(0,2), breaks=c(0,1,2)) +
  theme(axis.text.x = element_text(angle = 0, hjust = .5, vjust = .5))+ 
  labs(x = "Phase", y = "Number of Looks")  +
  ggthemes::theme_few() +
  langcog::scale_colour_solarized() 
```

```{r}
lmer_data <- d %>%
  filter(!exclude) %>%
  mutate(trial_type = factor(trial_type), 
         age_c = as.numeric(langcog::scale(age_months, scale=FALSE)),
         phase_name = factor(phase_name), 
         gaze = factor(Gaze))

maximal_mod <- lmer(num_looks ~ trial_type *  age_c * gaze * phase_name +
                           (trial_type | SID), 
                         data = lmer_data)

g_lm <- summary(maximal_mod)


lmer_data_halfs <- halfs %>%
  filter(!exclude) %>%
  mutate(trial_type = factor(trial_type), 
         age_c = as.numeric(langcog::scale(age_months, scale=FALSE)),
         phase_name = factor(phase_name), 
         gaze = factor(Gaze),
         first_half = factor(first_half))

maximal_mod <- lmer(num_looks ~ trial_type *  age_c * gaze * first_half * phase_name +
                           (trial_type | SID), 
                         data = lmer_data_halfs)

g_lm <- summary(maximal_mod)
```

Results of Experiment 2 are presented in Figure \ref{fig:results_e2}. Inter-rater reliability for the number of looks in each phase was again high, intraclass correlation *r* = .97, *p*<.001. To quantify the main and interactive effects of familiarity, gaze informativity, phase, and age on social referencing, we fit a mixed-effects linear regression model with the following structure: `number of looks ~ familiarity * age in months * gaze * phase + (familiarity | Subject ID)`. In contrast to Experiment 1, a model with phase as a predictor converged.

First, do children reference a speaker more often when the objects and label are novel? Phase interacted with familiarity such that the response phase of novel trials was associated with significantly more looks ($\beta$ = `r round(g_lm$coefficients[17], digits = 2)`, *p* < .001). This result is consistent with our finding from the analysis of the response phase in Experiment 1. However, in contrast to Experiment 1, we did not observe that looking was significantly greater for novel trials in the planning phase.

We were also interested in whether mutual exclusivity trials would elicit an intermediate amount of uncertainty. We observed a three-way interaction of familiarity, gaze, and phase, such that the response phase of mutual exclusivity trials in the no-referential-gaze condition was associated with significantly more looks ($\beta$ = `r round(g_lm$coefficients[36], digits = 2)`, *p* < .01). Thus, mutual exclusivity trials were associated with greater looking only when the experimenter did not provide informative gaze. This finding is intriguing given that children should be able to solve mutual exclusivity trials without gaze information. Instead, they appear to remain relatively uncertain while making a decision if excluding the familiar object is their only cue to reference, but this uncertainty is resolved if the speaker's gaze is informative. On the other hand, informative gaze during labeling did not lessen social referencing for novel trials, suggesting that gaze information alone was not sufficient to reduce uncertainty. Instead, both gaze information and mutual exclusivity provided evidence about a label-object pairing, and children required both types of evidence to feel certain about their response. 

Finally, we observed a four-way interaction such that the response phase of novel trials in the gaze condition was associated with more looking with increasing age ($\beta$ = `r round(g_lm$coefficients[46], digits = 2)`, *p* < .01), suggesting that children may become more selective in their social referencing as they get older. It may be that children improve in their ability to monitor the need for disambiguating information, or they may become more likely to recognize that social information can be a source of disambiguation. 

Lastly, we again did not find selective social referencing during the label phase, even when referential gaze was available. This result rules out the possibility that children were less selective during labeling because they learned that gaze direction was not informative. 

#General Discussion

During the preschool years, children are increasingly able to actively gather their own information through help-seeking and exploration [@Chouinard2007; @Schulz2007]. Do children monitor their own uncertainty to guide these behaviors, or are they indiscriminate with regard to underlying knowledge states? Here, we examined whether preschool-aged children's social referencing during a word-learning task was driven by uncertainty about a label's referent.

We found that referential ambiguity strongly predicted children's social referencing. Specifically, we observed this selectivity when children were forced to decide which object the speaker was referring to. We speculate that children referenced the speaker during the decision process because they expected confirmation of the accuracy of their choice, either implicitly through the adult’s facial expressions, or through explicit feedback. This idea is consistent with other recent research that has found that preschool-aged children seek help selectively when they are less likely to succeed, because a problem is difficult or because they are less skilled [@Vredenburgh2015].

Most intriguingly, we found that children's looking was driven by graded referential evidence. In the case of mutual exclusivity trials, children could solve the problem of reference by excluding the familiar item [@Markman1988]. Thus, unlike novel trials, they likely had some signal about the correct object-label mapping. If children simply monitored the presence or absence of such signals, they would have consistently treated mutual exclusivity trials as familiar trials. Instead, their social referencing depended on a combination of cues from mutual exclusivity and gaze informativity, suggesting that they are sensitive to graded evidence and seek disambiguating information only when uncertainty is relatively high. Children's greater social referencing on trials with only one cue to reference (i.e., mutual exclusivity trials with no referential gaze and novel trials with referential gaze) additionally suggests that children may remain uncertain about a new label-object mapping if they have not received confirmation of its accuracy, for example, through explicit feedback or gaze direction.

On the other hand, we found no evidence for selective social referencing as the object was being labeled. One possibility is that young children do not recognize the need for disambiguating information until they need to make a decision. Another possibility is that preschool-aged children spontaneously look at a speaker regardless of ambiguity, and additional looking was not needed or possible. Notably, Vaish et al. observed selective referencing during labeling among infants. Since infants in that study were holding one of the objects during labeling, referencing the speaker would have required them to disengage from that object, and may therefore have been more costly, promoting selectivity. Future research with preschoolers that includes a greater reward trade off between attentional options would help to distinguish among these possibilities. Overall, these results provide evidence that preschool-aged children monitor graded uncertainty in their mental representations and act on that uncertainty through spontaneous information-seeking. 

# Acknowledgements

We thank Veronica Cristiano for assisting with data collection. This work supported by a generous gift from Kinedu, Inc. 

# References 

```{r}

```

\setlength{\parindent}{-0.1in} 
\setlength{\leftskip}{0.125in}
\noindent
