---
title: "Social Referencing and Uncertainty, Experiment 2"
author: "Emily, Benny & Mike"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    number_sections: true
---

<style type="text/css">
body, td {
   font-size: 14px;
}
code {
  font-size: 11px;
}
pre {
  font-size: 11px;
}
</style>

Data analysis for Experiment 2 of social referencing study.
Gaze is manipulated between subjects.
Three trial types: familiar, novel, mutual exclusivity

# Data preprocessing

Preliminaries.

```{r echo=FALSE}
rm(list=ls())
setwd("~/Desktop/soc_ref_uncert/analysis")
knitr::opts_chunk$set(fig.width=8, fig.height=5, 
                      echo=TRUE, warning=FALSE, message=FALSE, cache=TRUE)
suppressPackageStartupMessages(c("dplyr","langcog","tidyr","ggplot2","lme4"))
library(langcog)
library(dplyr)
library(ggplot2)
library(rjson)
library(stringr)
library(tidyr)
library(lme4)
library(xtable)
library(knitr)
library(markdown)
theme_set(theme_bw())
```

Read in files and consolidate to the same directory. 

```{r}
d.raw <- data.frame()
files <- dir("../data_e2/coder_1")

for (f in files) {
  jf <- paste("../data_e2/coder_1/",f,sep="")
  jd <- read.csv(jf)
  
  id <- data.frame(SID = f,
                   line = jd$phase.ordinal,
                   phase = as.numeric(jd$phase.1_2_3_4),
                   phase_onset = jd$phase.onset,
                   phase_offset = jd$phase.offset, 
                   num_looks = jd$reference.num_looks,
                   num_ques = as.numeric(jd$reference.num_ques),
                   num_sou = jd$reference.num_SOU,
                   exclude = as.numeric(jd$reference.exclude))
  d.raw <- bind_rows(d.raw, id)}

d.raw$SID <- str_replace(d.raw$SID, ".csv", "")
d.raw <- distinct(d.raw)
```

Read in trial info and demographics. 

```{r}
demo <- read.csv("../demo_soc_ref_uncert_exp2.csv") 
demo$age <- as.numeric(demo$age)
demo$age_years <- trunc(demo$age, digits = 0)
demo$age_months <- demo$age*12
demo$Condition <- str_replace(demo$Condition, " ", "")

trial_info <- read.csv("trial_info_e2.csv")
```

Join trial info and demographics with raw data.

```{r}
d <- left_join(d.raw, demo) %>%
  select(SID, phase, num_looks, num_ques, num_sou, exclude, age_years, age_months, gender, line, Condition, Gaze, phase_onset, phase_offset) %>%
  mutate(phase_length = phase_offset - phase_onset) %>%
  mutate(social_ref = as.numeric(num_looks>0))%>%
  left_join(trial_info, by = c("Condition","line"))%>%
  mutate(first_half = between(trial, 1, 4)) 

d <- d %>%
  filter(phase_length > 50) %>%
  filter(age_years > 2) %>%
  mutate(looks_sec = (num_looks/phase_length)*1000)
```

Plot social referencing by trial type (familiar, novel, mutual exclusivity) and presence of referential gaze.

Get means.
```{r}
#get means for participants by condition for number of looks
msslooks <- filter(d, exclude == 0) %>%
  group_by(SID, phase_name, trial_type, Gaze, age_years) %>%
  summarise(num_looks = mean(num_looks))

#get means and CIs across participants for number of looks
mslooks <- filter(d, exclude == 0) %>%
  group_by(phase_name, trial_type, Gaze, age_years) %>%
  multi_boot_standard(col = "num_looks") 

msslooks$phase_name <- factor(msslooks$phase_name, levels = c("label-begin_slide","begin_slide-end_slide","end_slide-touch","touch-release"))

mslooks$phase_name <- factor(mslooks$phase_name, levels = c("label-begin_slide","begin_slide-end_slide","end_slide-touch","touch-release"))
```


##T-tests.
```{r}
t <- msslooks 
t$age <- str_replace(t$age_years, "3", "three")
t$age <- str_replace(t$age, "4", "four")
t <- t %>%
  spread(trial_type, num_looks)
```

T-tests: Novel vs. Familiar vs. Mutual for Gaze, Touch phase

```{r}
#Novel vs. Familiar, Gaze, 4-year-olds
t.test(subset(t$novel, t$phase_name == "end_slide-touch" & t$age == "four" & t$Gaze == "gaze"),subset(t$familiar, t$phase_name == "end_slide-touch" & t$age == "four" & t$Gaze == "gaze"), paired = TRUE)

#Novel vs. Mutual, Gaze, 4-year-olds
t.test(subset(t$novel, t$phase_name == "end_slide-touch" & t$age == "four" & t$Gaze == "gaze"),subset(t$mutual, t$phase_name == "end_slide-touch" & t$age == "four" & t$Gaze == "gaze"), paired = TRUE)

#Familiar vs. Mutual, Gaze, 4-year-olds
t.test(subset(t$familiar, t$phase_name == "end_slide-touch" & t$age == "four" & t$Gaze == "gaze"),subset(t$mutual, t$phase_name == "end_slide-touch" & t$age == "four" & t$Gaze == "gaze"), paired = TRUE)

#Novel vs. Familiar, Gaze, 3-year-olds
t.test(subset(t$novel, t$phase_name == "end_slide-touch" & t$age == "three" & t$Gaze == "gaze"),subset(t$familiar, t$phase_name == "end_slide-touch" & t$age == "three" & t$Gaze == "gaze"), paired = TRUE)

#Novel vs. Mutual, Gaze, 3-year-olds
t.test(subset(t$novel, t$phase_name == "end_slide-touch" & t$age == "three" & t$Gaze == "gaze"),subset(t$mutual, t$phase_name == "end_slide-touch" & t$age == "three" & t$Gaze == "gaze"), paired = TRUE)

#Familiar vs. Mutual, Gaze, 3-year-olds
t.test(subset(t$familiar, t$phase_name == "end_slide-touch" & t$age == "three" & t$Gaze == "gaze"),subset(t$mutual, t$phase_name == "end_slide-touch" & t$age == "three" & t$Gaze == "gaze"), paired = TRUE)
```

T-tests: Novel vs. Familiar vs. Mutual for Gaze, Response phase

```{r}
#Novel vs. Familiar, Gaze, 4-year-olds,
t.test(subset(t$novel, t$phase_name == "touch-release" & t$age == "four" & t$Gaze == "gaze"),subset(t$familiar, t$phase_name == "touch-release" & t$age == "four" & t$Gaze == "gaze"), paired = TRUE)

#Novel vs. Mutual, Gaze, 4-year-olds
t.test(subset(t$novel, t$phase_name == "touch-release" & t$age == "four" & t$Gaze == "gaze"),subset(t$mutual, t$phase_name == "touch-release" & t$age == "four" & t$Gaze == "gaze"), paired = TRUE)

#Familiar vs. Mutual, Gaze, 4-year-olds
t.test(subset(t$familiar, t$phase_name == "touch-release" & t$age == "four" & t$Gaze == "gaze"),subset(t$mutual, t$phase_name == "touch-release" & t$age == "four" & t$Gaze == "gaze"), paired = TRUE)

#Novel vs. Familiar, Gaze, 3-year-olds,
t.test(subset(t$novel, t$phase_name == "touch-release" & t$age == "three" & t$Gaze == "gaze"),subset(t$familiar, t$phase_name == "touch-release" & t$age == "three" & t$Gaze == "gaze"), paired = TRUE)

#Novel vs. Mutual, Gaze, 3-year-olds
t.test(subset(t$novel, t$phase_name == "touch-release" & t$age == "three" & t$Gaze == "gaze"),subset(t$mutual, t$phase_name == "touch-release" & t$age == "three" & t$Gaze == "gaze"), paired = TRUE)

#Familiar vs. Mutual, Gaze, 3-year-olds
t.test(subset(t$familiar, t$phase_name == "touch-release" & t$age == "three" & t$Gaze == "gaze"),subset(t$mutual, t$phase_name == "touch-release" & t$age == "three" & t$Gaze == "gaze"), paired = TRUE)
```

T-tests: Novel vs. Familiar vs. Mutual for No-Gaze, Touch phase

```{r}
#Novel vs. Familiar, Gaze, 4-year-olds
t.test(subset(t$novel, t$phase_name == "end_slide-touch" & t$age == "four" & t$Gaze == "no_gaze"),subset(t$familiar, t$phase_name == "end_slide-touch" & t$age == "four" & t$Gaze == "no_gaze"), paired = TRUE)

#Novel vs. Mutual, Gaze, 4-year-olds
t.test(subset(t$novel, t$phase_name == "end_slide-touch" & t$age == "four" & t$Gaze == "no_gaze"),subset(t$mutual, t$phase_name == "end_slide-touch" & t$age == "four" & t$Gaze == "no_gaze"), paired = TRUE)

#Familiar vs. Mutual, Gaze, 4-year-olds
t.test(subset(t$familiar, t$phase_name == "end_slide-touch" & t$age == "four" & t$Gaze == "no_gaze"),subset(t$mutual, t$phase_name == "end_slide-touch" & t$age == "four" & t$Gaze == "no_gaze"), paired = TRUE)

#Novel vs. Familiar, Gaze, 3-year-olds
t.test(subset(t$novel, t$phase_name == "end_slide-touch" & t$age == "three" & t$Gaze == "no_gaze"),subset(t$familiar, t$phase_name == "end_slide-touch" & t$age == "three" & t$Gaze == "no_gaze"), paired = TRUE)

#Novel vs. Mutual, Gaze, 3-year-olds
t.test(subset(t$novel, t$phase_name == "end_slide-touch" & t$age == "three" & t$Gaze == "no_gaze"),subset(t$mutual, t$phase_name == "end_slide-touch" & t$age == "three" & t$Gaze == "no_gaze"), paired = TRUE)

#Familiar vs. Mutual, Gaze, 3-year-olds
t.test(subset(t$familiar, t$phase_name == "end_slide-touch" & t$age == "three" & t$Gaze == "no_gaze"),subset(t$mutual, t$phase_name == "end_slide-touch" & t$age == "three" & t$Gaze == "no_gaze"), paired = TRUE)
```

T-tests: Novel vs. Familiar vs. Mutual for No-Gaze, Response phase

```{r}
#Novel vs. Familiar, Gaze, 4-year-olds, Touch phase
t.test(subset(t$novel, t$phase_name == "touch-release" & t$age == "four" & t$Gaze == "no_gaze"),subset(t$familiar, t$phase_name == "touch-release" & t$age == "four" & t$Gaze == "no_gaze"), paired = TRUE)

#Novel vs. Mutual, Gaze, 4-year-olds
t.test(subset(t$novel, t$phase_name == "touch-release" & t$age == "four" & t$Gaze == "no_gaze"),subset(t$mutual, t$phase_name == "touch-release" & t$age == "four" & t$Gaze == "no_gaze"), paired = TRUE)

#Familiar vs. Mutual, Gaze, 4-year-olds
t.test(subset(t$familiar, t$phase_name == "touch-release" & t$age == "four" & t$Gaze == "no_gaze"),subset(t$mutual, t$phase_name == "touch-release" & t$age == "four" & t$Gaze == "no_gaze"), paired = TRUE)

#Novel vs. Familiar, Gaze, 3-year-olds, Touch phase
t.test(subset(t$novel, t$phase_name == "touch-release" & t$age == "three" & t$Gaze == "no_gaze"),subset(t$familiar, t$phase_name == "touch-release" & t$age == "three" & t$Gaze == "no_gaze"), paired = TRUE)

#Novel vs. Mutual, Gaze, 3-year-olds
t.test(subset(t$novel, t$phase_name == "touch-release" & t$age == "three" & t$Gaze == "no_gaze"),subset(t$mutual, t$phase_name == "touch-release" & t$age == "three" & t$Gaze == "no_gaze"), paired = TRUE)

#Familiar vs. Mutual, Gaze, 3-year-olds
t.test(subset(t$familiar, t$phase_name == "touch-release" & t$age == "three" & t$Gaze == "no_gaze"),subset(t$mutual, t$phase_name == "touch-release" & t$age == "three" & t$Gaze == "no_gaze"), paired = TRUE)
```

Looks per second. Do not prefer this measure- I think response time and looking behavior are meaningfully correlated.
```{r}
#get means for participants by condition for number of looks
msslooks <- filter(d, exclude == 0) %>%
  group_by(SID, phase_name, trial_type,  age_years, Gaze) %>%
  summarise(looks_sec = mean(looks_sec))

#get means and CIs across participants for number of looks
mslooks <- filter(d, exclude == 0) %>%
  group_by(phase_name, trial_type, age_years, Gaze) %>%
  multi_boot_standard(col = "looks_sec", na.rm = TRUE) 

msslooks$phase_name <- factor(msslooks$phase_name, levels = c("label-begin_slide","begin_slide-end_slide","end_slide-touch","touch-release"))

mslooks$phase_name <- factor(mslooks$phase_name, levels = c("label-begin_slide","begin_slide-end_slide","end_slide-touch","touch-release"))

#plot looks per second.
ggplot(msslooks, aes(x = phase_name, y = looks_sec, 
               col = trial_type, group = trial_type)) + 
  geom_line(data = mslooks, aes(y = mean)) + 
  geom_pointrange(data = mslooks, 
                  aes(y = mean, ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width =.1)) + 
  facet_grid(age_years ~Gaze) + 
  ylim(c(0,1)) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5))
```

Get mean questions for plots.
```{r}
mssques <- filter(d, exclude == 0) %>%
  group_by(SID, phase_name, trial_type, Gaze, age_years) %>%
  summarise(num_ques = mean(num_ques))

msques <- filter(d, exclude == 0) %>%
  group_by(phase_name, trial_type, Gaze, age_years) %>%
  multi_boot_standard(col = "num_ques") 

mssques$phase_name <- factor(mssques$phase_name, levels = c("label-begin_slide","begin_slide-end_slide","end_slide-touch","touch-release"))

msques$phase_name <- factor(msques$phase_name, levels = c("label-begin_slide","begin_slide-end_slide","end_slide-touch","touch-release"))
```

Get mean statements of ignorance for plots.
```{r}
msssou <- filter(d, exclude == 0) %>%
  group_by(SID, phase_name, trial_type, Gaze, age_years) %>%
  summarise(num_sou = mean(num_sou))

mssou <- filter(d, exclude == 0) %>%
  group_by(phase_name, trial_type, Gaze, age_years) %>%
  multi_boot_standard(col = "num_sou") 

msssou$phase_name <- factor(msssou$phase_name, levels = c("label-begin_slide","begin_slide-end_slide","end_slide-touch","touch-release"))

mssou$phase_name <- factor(mssou$phase_name, levels = c("label-begin_slide","begin_slide-end_slide","end_slide-touch","touch-release"))
```

Plots.
```{r}
#plot number of questions.
ggplot(mssques, aes(x = phase_name, y = num_ques, 
               col = trial_type, group = trial_type)) + 
  geom_line(data = msques, aes(y = mean)) + 
  geom_pointrange(data = msques, 
                  aes(y = mean, ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width =.1)) + 
  facet_grid(age_years ~ Gaze) + 
  ylim(c(0,1.5)) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5))

#plot number of statements of uncertainty.
ggplot(msssou, aes(x = phase_name, y = num_sou, 
               col = trial_type, group = trial_type)) + 
  geom_line(data = mssou, aes(y = mean)) + 
  geom_pointrange(data = mssou, 
                  aes(y = mean, ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width =.1)) + 
  facet_grid(age_years ~ Gaze) + 
  ylim(c(0,.25)) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5))
```

#Planned analyses

```{r}
#separate linear models for each phase

# lb_maximal_mod <- lmer(num_looks ~ trial_type * age_years +
#                            (trial_type | SID), 
#                          data = filter(d, 
#                                        exclude == 0, 
#                                        phase_name == "label-begin_slide"))
# 
# be_maximal_mod <- lmer(num_looks ~ trial_type * Gaze * age_years +
#                            (trial_type * Gaze | SID), 
#                          data = filter(d, 
#                                        exclude == 0, 
#                                        phase_name == "begin_slide-end_slide"))
# 
# st_maximal_mod <- lmer(num_looks ~ trial_type * Gaze * scale(age_months) +
#                            (trial_type * Gaze | SID), 
#                          data = filter(d, 
#                                        exclude == 0, 
#                                        phase_name == "end_slide-touch"))

tr_maximal_mod <- lmer(num_looks ~ trial_type *  age_years +
                           (1| SID), 
                         data = filter(d, 
                                       exclude == 0, 
                                       phase_name == "touch-release", 
                                       Gaze == "gaze"))

tr_maximal_mod <- lmer(num_looks ~ trial_type *  age_years +
                           (1| SID), 
                         data = filter(d, 
                                       exclude == 0, 
                                       phase_name == "touch-release", 
                                       Gaze == "no_gaze"))



# maximal model; does not converge
# omni_maximal_mod <- lmer(num_looks ~ factor(trial_type) * Gaze * 
#                            scale(age_months) * phase_name +
#                            (trial_type + Gaze + phase_name | SID), 
#                          data = filter(d, exclude == 0))
```

#Conclusions
